%-------------------------
% Resume in Latex
% Author : Haesung Lee
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Haesung Lee} \\ \vspace{1pt}
    \small (+82) 10-5641-3844 $|$ \href{mailto:edwin109802@gmail.com}{\underline{edwin109802@gmail.com}} $|$
    \href{https://github.com/lshtar13}{\underline{github.com/lshtar13}}
\end{center}

\section{Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \item 
      \small{Computer Science undergraduate with experience in web development, especially backend engineering, and research. 
      Currently interested in backend engineering, blockchain, and operating system development.}
  \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sungkyunkwan University}{Suwon, South Korea}
      {Bachelor of Computer Science and Engineering}{Feb. 2022 -- Present}
      \resumeSubItem{GPA(Major): 4.14(4.34)/4.5}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineering Intern}{Oct. 2025 -- Present}
      {Blockchain Dept., Shinhan Securities}{Seoul, South Korea}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{microservices} for a \textbf{high-frequency trading} platform.}
        \resumeItem{Developed backend services with \textbf{Python, gRPC, and FastAPI} for \textbf{trading bots} and researched cryptocurrency arbitrage strategies.}
      \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Researcher}{Aug. 2023 -- Feb. 2024}
      {Intelligent Embedded Systems Research Lab., Sungkyunkwan University}{Suwon, South Korea}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{selective journaling} scheme for the \textbf{ext4} file system to dynamically mitigate \textbf{fsync latency} based on I/O request intervals.}
        \resumeItem{Improved \textbf{robustness across I/O workloads} (8KiB--4MiB) 
        by keeping \textbf{average fsync latency} consistently lower than both \textbf{fast\_commit} and \textbf{normal\_only} baselines 
        and reduced \textbf{maximum fsync latency} across all workloads compared to baselines.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Artificial Intelligence Engineering Intern}{Jun. 2023 -- Aug. 2023}
      {SOYNET Co,Ltd.}{Seongnam, South Korea}
      \resumeItemListStart
        \resumeItem{Analyzed and ported open sourced deep learning models such as \textbf{YOLOv7} from PyTorch to an in-house \textbf{C++/CUDA} inference engine, achieving \textbf{3.5$\times$ faster inference} and \textbf{2.7$\times$ lower GPU memory usage}.}
        \resumeItem{Trained and fine-tuned deep learning models such as \textbf{MagFace} for object detection and segmentation tasks, improving accuracy on internal benchmarks.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{\href{https://github.com/skkuding/codedang}{Codedang}} $|$ \emph{Typescript, Go, NestJS, Prisma, Docker, Redis, RabbitMQ, GraphQL, Git}}{Aug. 2022 -- Feb. 2024}
          \resumeItemListStart
            \resumeItem{Developed \textbf{RESTful APIs} for an \textbf{online judge} platform using \textbf{NestJS} and \textbf{Prisma ORM}.}
            \resumeItem{Refactored legacy admin services from \textbf{RESTful API} to \textbf{GraphQL}.}
            \resumeItem{Built a scalable \textbf{asynchronous code evaluation system} in \textbf{Go} with \textbf{RabbitMQ} to handle high-concurrency submissions.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{\href{https://github.com/HOYNET/Fin2Vec}{Fin2Vec}} $|$ \emph{Python, PyTorch, Conda, Matplotlib}}{Aug. 2023 -- Nov. 2023}
          \resumeItemListStart
            \resumeItem{Built a \textbf{transformer-based model} (\textbf{Fin2Vec}) that turns \textbf{financial time series} data into meaningful embeddings using attention mechanisms.}
            \resumeItem{Developed \textbf{clustering and visualization tools} to analyze stock market trends based on learned embeddings and Bloomberg data.}
            \resumeItem{Designed an \textbf{end-to-end training and inference pipeline} using \textbf{PyTorch}, standardizing hyperparameter tuning experiments.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{\href{https://github.com/EdgeCrafters}{Edged Judger Platform}} $|$ \emph{C, CMake, Git}}{Jul. 2023 -- Sep. 2023}
          \resumeItemListStart
            \resumeItem{Designed a \textbf{lightweight and secure code-judging sandbox} environment for \textbf{educational use}, isolating user code execution at the OS level.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, Python, C/C++, TypeScript} \\
     \textbf{Frameworks}{: Node.js, NextJS, FastAPI, gRPC, Apollo} \\
     \textbf{Libraries}{: CCXT, PyTorch, pandas, NumPy, Matplotlib} \\
     \textbf{Developer Tools}{: Git, Docker, Redis, RabbitMQ, GDB, Postman, Bruno, Linux, Vim} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
